Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
to include

<!-- TODO: missing results -->

@@

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales <!-- TODO: add fig 6-->. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat type as in
Figure \@ref(fig:lcres). Since habitat data are available across a range of
spatial scales, we evaluated the influence of increasing spatial resolution on
multilayer network metrics. As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
open layer had greater individual variation in graph strength, and foraging
layers showed an increase in graph strength with increasing spatial resolution
(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
on Fogo Island and the proportion of relocations in foraging habitat decreased
as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
the foraging layer had similar edge overlap as the open layer at 30 m resolution 
indicating its importance in caribou sociality. As such, multilayer network
measures related to habitat are explicitly dependent on spatial scale.  If the
spatial resolution of the habitat data are insufficient to capture rare
habitats, for example, context-specific relationships between individuals may
not be captured.
<!-- habitat+social -->

>>>>

<!-- TODO: missing results

As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
open layer had greater individual variation in graph strength, and foraging
layers showed an increase in graph strength with increasing spatial resolution
(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
on Fogo Island and the proportion of relocations in foraging habitat decreased
as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
the foraging layer had similar edge overlap as the open layer at 30 m resolution 
indicating its importance in caribou sociality. 
-->

@@
